---
title: "FinalProject"
author: "XinyiYu"
date: "2025-10-16"
output:
  pdf_document: default
  html_document: default
---
packages
```{r}
library(readxl)
library(dplyr)
library(readr)
library(stringr)
library(ggplot2)
```


CDC Pregnancy Vaccination
```{r}
#了Use Webscraping or an API for Data Collection
vacc_url <- "https://data.cdc.gov/api/views/h7pm-wmjc/rows.csv?accessType=DOWNLOAD"
vacc_df <- read.csv(vacc_url)

#uniform NY
vacc_df$Geography <- gsub("NY-City of New York", "New York", vacc_df$Geography)
vacc_df$Geography <- gsub("NY-Rest of state", "New York", vacc_df$Geography)

#eliminate others
vacc_df <- vacc_df %>%
  filter(!(Geography %in% c("United States", "Puerto Rico", "Commonwealth of the Northern Mariana Islands")))

#State name to abbreviation
state_abbrev <- c(
  'Alabama' = 'AL', 'Alaska' = 'AK', 'Arizona' = 'AZ', 'Arkansas' = 'AR',
  'California' = 'CA', 'Colorado' = 'CO', 'Connecticut' = 'CT', 'Delaware' = 'DE',
  'District of Columbia' = 'DC', 'Florida' = 'FL', 'Georgia' = 'GA', 'Hawaii' = 'HI',
  'Idaho' = 'ID', 'Illinois' = 'IL', 'Indiana' = 'IN', 'Iowa' = 'IA', 'Kansas' = 'KS',
  'Kentucky' = 'KY', 'Louisiana' = 'LA', 'Maine' = 'ME', 'Maryland' = 'MD',
  'Massachusetts' = 'MA', 'Michigan' = 'MI', 'Minnesota' = 'MN',
  'Mississippi' = 'MS', 'Missouri' = 'MO', 'Montana' = 'MT', 'Nebraska' = 'NE',
  'Nevada' = 'NV', 'New Hampshire' = 'NH', 'New Jersey' = 'NJ',
  'New Mexico' = 'NM', 'New York' = 'NY', 'North Carolina' = 'NC',
  'North Dakota' = 'ND', 'Ohio' = 'OH', 'Oklahoma' = 'OK', 'Oregon' = 'OR',
  'Pennsylvania' = 'PA', 'Rhode Island' = 'RI', 'South Carolina' = 'SC',
  'South Dakota' = 'SD', 'Tennessee' = 'TN', 'Texas' = 'TX', 'Utah' = 'UT',
  'Vermont' = 'VT', 'Virginia' = 'VA', 'Washington' = 'WA',
  'West Virginia' = 'WV', 'Wisconsin' = 'WI', 'Wyoming' = 'WY'
)

# add abbreviation column
vacc_df <- vacc_df %>%
  mutate(State = state_abbrev[Geography])
write_csv(vacc_df, "vaccination.csv")
head(vacc_df)
```


Urban-Rural Processing
```{r}
# Down load Urban-Rural
url <- "https://www.cdc.gov/nchs/data/data-analysis/NCHSurb-rural-codes.csv"
download.file(url, destfile = "urban_rural.xlsx", mode = "wb")
urban_rural <- read_csv("/Users/yuxinyi/Dartmouth/data wrangling/finalProject/urban_rural.csv")

#eliminate NA
urban_rural <- urban_rural %>%
  select(ST_ABBREV, CTYPOP, CODE2013, CODE2023) %>%
  filter(!is.na(CTYPOP), !is.na(CODE2013), !is.na(CODE2023))

# Calculate total state population
state_pop <- urban_rural %>%
  group_by(ST_ABBREV) %>%
  summarise(STATEPOP = sum(CTYPOP, na.rm = TRUE))

# Combine the total population and calculate the weight
urban_rural <- urban_rural %>%
  left_join(state_pop, by = "ST_ABBREV") %>%
  mutate(WEIGHT = CTYPOP / STATEPOP,
         INDEX2013 = CODE2013 * WEIGHT,
         INDEX2023 = CODE2023 * WEIGHT)

# Calculation of weighted urban and rural index & changes in 2013 and 2023
urban_result <- urban_rural %>%
  group_by(ST_ABBREV) %>%
  summarise(INDEX2013 = sum(INDEX2013),
            INDEX2023 = sum(INDEX2023)) %>%
  mutate(CHANGE = INDEX2023 - INDEX2013) %>%
  arrange(desc(CHANGE))
head(urban_result)

write.csv(urban_result, "state_urban_index_2013_2023.csv", row.names = FALSE)

```

insurance coverage
```{r}
folder <- "/Users/yuxinyi/Dartmouth/data wrangling"
years <- setdiff(2012:2022, 2020)  # skip year 2020

# State name to abbreviation
state_abbrev <- c(
  'Alabama' = 'AL', 'Alaska' = 'AK', 'Arizona' = 'AZ', 'Arkansas' = 'AR',
  'California' = 'CA', 'Colorado' = 'CO', 'Connecticut' = 'CT', 'Delaware' = 'DE',
  'District of Columbia' = 'DC', 'Florida' = 'FL', 'Georgia' = 'GA', 'Hawaii' = 'HI',
  'Idaho' = 'ID', 'Illinois' = 'IL', 'Indiana' = 'IN', 'Iowa' = 'IA', 'Kansas' = 'KS',
  'Kentucky' = 'KY', 'Louisiana' = 'LA', 'Maine' = 'ME', 'Maryland' = 'MD',
  'Massachusetts' = 'MA', 'Michigan' = 'MI', 'Minnesota' = 'MN',
  'Mississippi' = 'MS', 'Missouri' = 'MO', 'Montana' = 'MT', 'Nebraska' = 'NE',
  'Nevada' = 'NV', 'New Hampshire' = 'NH', 'New Jersey' = 'NJ',
  'New Mexico' = 'NM', 'New York' = 'NY', 'North Carolina' = 'NC',
  'North Dakota' = 'ND', 'Ohio' = 'OH', 'Oklahoma' = 'OK', 'Oregon' = 'OR',
  'Pennsylvania' = 'PA', 'Rhode Island' = 'RI', 'South Carolina' = 'SC',
  'South Dakota' = 'SD', 'Tennessee' = 'TN', 'Texas' = 'TX', 'Utah' = 'UT',
  'Vermont' = 'VT', 'Virginia' = 'VA', 'Washington' = 'WA',
  'West Virginia' = 'WV', 'Wisconsin' = 'WI', 'Wyoming' = 'WY'
)

all_data <- list()

#Loop to read all year data in one go
for (year in years) {
  file_path <- file.path(folder, paste0("raw_data", year, ".csv"))
  
  try({
    #Use col_types to explicitly specify the format and skip the Footnotes and Total columns (not used)
    df <- read_csv(
      file_path,
      skip = 2,
      col_types = cols(
        Location = col_character(),
        Employer = col_double(),
        `Non-Group` = col_double(),
        Medicaid = col_double(),
        Medicare = col_double(),
        Military = col_double(),
        Uninsured = col_double(),
        Total = col_skip(),
        Footnotes = col_skip()
      )
    )
    # Keep only the state-level rows and remove the united state row.
    df <- df %>%
      filter(Location %in% names(state_abbrev))
    #Add year and state abbreviations
    df <- df %>%
      mutate(
        Year = year,
        State = state_abbrev[Location],
        Insured = Employer + `Non-Group` + Medicaid + Medicare + Military
      ) %>%
      select(Year, State, Insured, Uninsured)

    #summarizing
    all_data[[as.character(year)]] <- df
    message("Processed ", year, " with ", nrow(df), " rows")
    
  }, silent = TRUE)
}

#merge
insurance <- bind_rows(all_data)

write_csv(insurance, "insurance_summary_by_state_2012_2022.csv")
head(insurance)
```

merge
```{r}
#urban_rural only retains 2023. urban_merge is the version used for merge and is not saved as csv.
urban_merge <- urban_result %>%
  select(ST_ABBREV, INDEX2023) %>%
  rename(State = ST_ABBREV,
         UrbanicityIndex = INDEX2023)
#merge
merged_df <- vacc_df %>%
  mutate(Year = as.numeric(`Survey.Year.Influenza.Season`)) %>%
  left_join(insurance, by = c("State", "Year")) %>%
  left_join(urban_merge, by = "State")
head(merged_df)
write_csv(merged_df, "MergedVersion.csv")
```

clean & simplify for regression
```{r}
#clean
merged_clean <- merged_df %>%
  filter(!is.na(Estimate....), !is.na(Uninsured), !is.na(Insured), 
         !Estimate.... %in% c("NR*", "N/A", "--", "*")) %>% #ignore "NR*" in Estimate.... due to "NR*" represent the samples are too small and will influence following analysis
  mutate(
    Year = as.numeric(Survey.Year.Influenza.Season),
    Coverage = as.numeric(str_replace(Estimate...., "%", "")),
    UninsuredRate = Uninsured / (Insured + Uninsured)
  )

# simplify
merged_summary <- merged_clean %>%
  group_by(State, Year, Vaccine) %>%
  summarise(
    Coverage = mean(Coverage, na.rm = TRUE), 
    UninsuredRate = mean(UninsuredRate, na.rm = TRUE),
    UrbanicityIndex = first(UrbanicityIndex)
  ) %>%
  ungroup()
head(merged_summary)
```
Influenza visualization&modeling
```{r}
merged_summary %>%
  filter(Vaccine == "Influenza") %>%
  ggplot(aes(x = UninsuredRate, y = Coverage)) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE, color = "blue") +
  labs(
    title = "Influenza Vaccination vs Uninsured Rate",
    x = "Uninsured Rate",
    y = "Vaccination Coverage (%)"
  )
```

```{r}
model_flu <- lm(Coverage ~ UninsuredRate, data = merged_summary %>% filter(Vaccine == "Influenza"))
summary(model_flu)
```

Tdap visualization&modeling
```{r}
merged_summary %>%
  filter(Vaccine == "Tdap") %>%
  ggplot(aes(x = UninsuredRate, y = Coverage)) +
  geom_point(color = "black") +
  geom_smooth(method = "lm", color = "darkred", se = TRUE) +
  labs(
    title = "Tdap Vaccination vs Uninsured Rate",
    x = "Uninsured Rate",
    y = "Vaccination Coverage (%)"
  )
```
```{r}
tdap_model <- lm(Coverage ~ UninsuredRate, data = merged_summary %>% filter(Vaccine == "Tdap"))
summary(tdap_model)
```

Stratified Analysis by Race for Influenza Vaccination
Influenza&race
```{r}
influenza_race <- merged_df %>%
  filter(
    Vaccine == "Influenza",
    Dimension.Type == "Race and Ethnicity",
    !is.na(Estimate....),
    !Estimate.... %in% c("NR*", "N/A", "--", "*")
  ) %>%
  mutate(
    Coverage = as.numeric(str_replace(Estimate...., "%", "")),
    Year = as.numeric(Survey.Year.Influenza.Season),
    UninsuredRate = Uninsured / (Insured + Uninsured)
  )
unique(influenza_race$Dimension)
```
White, Non-Hispanic
```{r}
influenza_white <- influenza_race %>%
  filter(Dimension == "White, Non-Hispanic")
#plot
ggplot(influenza_white, aes(x = UninsuredRate, y = Coverage)) +
  geom_point(color = "steelblue", size = 2) +
  geom_smooth(method = "lm", se = TRUE, color = "darkred") +
  labs(
    title = "Influenza Coverage vs Uninsured Rate (White, Non-Hispanic)",
    x = "Uninsured Rate",
    y = "Vaccination Coverage (%)"
  ) +
  theme_minimal()
#summary
summary(lm(Coverage ~ UninsuredRate, data = influenza_white))

```
Black, Non-Hispanic
```{r}
influenza_black <- influenza_race %>%
  filter(Dimension == "Black, Non-Hispanic")
#plot
ggplot(influenza_black, aes(x = UninsuredRate, y = Coverage)) +
  geom_point(color = "forestgreen", size = 2) +
  geom_smooth(method = "lm", se = TRUE, color = "darkred") +
  labs(
    title = "Influenza Coverage vs Uninsured Rate (Black, Non-Hispanic)",
    x = "Uninsured Rate",
    y = "Vaccination Coverage (%)"
  ) +
  theme_minimal()
#summary
summary(lm(Coverage ~ UninsuredRate, data = influenza_black))
```
Hispanic
```{r}
influenza_hispanic <- influenza_race %>%
  filter(Dimension == "Hispanic")
#plot
ggplot(influenza_hispanic, aes(x = UninsuredRate, y = Coverage)) +
  geom_point(color = "orange", size = 2) +
  geom_smooth(method = "lm", se = TRUE, color = "darkred") +
  labs(
    title = "Influenza Coverage vs Uninsured Rate (Hispanic)",
    x = "Uninsured Rate",
    y = "Vaccination Coverage (%)"
  ) +
  theme_minimal()
#summary
summary(lm(Coverage ~ UninsuredRate, data = influenza_hispanic))
```
Other or Multiple Races, Non-Hispanic
```{r}
influenza_other <- influenza_race %>%
  filter(Dimension == "Other or Multiple Races, Non-Hispanic")
#plot
ggplot(influenza_other, aes(x = UninsuredRate, y = Coverage)) +
  geom_point(color = "purple", size = 2) +
  geom_smooth(method = "lm", se = TRUE, color = "darkred") +
  labs(title = "Influenza Coverage vs Uninsured Rate (Other or Multiple Races, Non-Hispanic)",
    x = "Uninsured Rate",
    y = "Vaccination Coverage (%)"
  ) +
  theme_minimal()
#summary
summary(lm(Coverage ~ UninsuredRate, data = influenza_other))
```
Merged Influenza Stratified by Race

```{r}
my_colors <- c(
  "White, Non-Hispanic" = "#44d8ee",
  "Black, Non-Hispanic" = "#679436",
  "Hispanic" = "#be0aff",   
  "Other or Multiple Races, Non-Hispanic" = "#f46197" 
)

ggplot(influenza_race, aes(
  x = UninsuredRate,
  y = Coverage,
  color = Dimension,
  shape = Dimension
)) +
  geom_point(size = 2, alpha = 0.6) + 
  geom_smooth(method = "lm", se = TRUE, fullrange = TRUE) +
  scale_color_manual(values = my_colors) + 
  labs(
    title = "Influenza Coverage vs Uninsured Rate by Race/Ethnicity",
    x = "Uninsured Rate",
    y = "Vaccination Coverage (%)",
    color = "Race/Ethnicity",
    shape = "Race/Ethnicity"
  ) +
  theme_classic() +
  guides(color = guide_legend(override.aes = list(size = 3))) +
  theme(
    legend.text = element_text(size = 5),
    legend.title = element_text(size = 6),
    legend.key.size = unit(0.6, "lines")
  )
```


Tdap&Race
```{r}
Tdap_race <- merged_df %>%
  filter(
    Vaccine == "Tdap",
    Dimension.Type == "Race and Ethnicity",
    !is.na(Estimate....),
    !Estimate.... %in% c("NR*", "N/A", "--", "*")
  ) %>%
  mutate(
    Coverage = as.numeric(str_replace(Estimate...., "%", "")),
    Year = as.numeric(Survey.Year.Influenza.Season),
    UninsuredRate = Uninsured / (Insured + Uninsured)
  )
unique(Tdap_race$Dimension)
```
White, Non-Hispanic
```{r}
Tdap_white <- Tdap_race %>%
  filter(Dimension == "White, Non-Hispanic")
#plot
ggplot(Tdap_white, aes(x = UninsuredRate, y = Coverage)) +
  geom_point(color = "steelblue", size = 2) +
  geom_smooth(method = "lm", se = TRUE, color = "darkred") +
  labs(
    title = "Tdap Coverage vs Uninsured Rate (White, Non-Hispanic)",
    x = "Uninsured Rate",
    y = "Vaccination Coverage (%)"
  ) +
  theme_minimal()
#summary
summary(lm(Coverage ~ UninsuredRate, data = Tdap_white))

```
Black, Non-Hispanic
```{r}
Tdap_black <- Tdap_race %>%
  filter(Dimension == "Black, Non-Hispanic")
#plot
ggplot(Tdap_black, aes(x = UninsuredRate, y = Coverage)) +
  geom_point(color = "forestgreen", size = 2) +
  geom_smooth(method = "lm", se = TRUE, color = "darkred") +
  labs(title = "Tdap Coverage vs Uninsured Rate (Black, Non-Hispanic)",
    x = "Uninsured Rate",
    y = "Vaccination Coverage (%)"
  ) +
  theme_minimal()
#summary
summary(lm(Coverage ~ UninsuredRate, data =Tdap_black))
```
Hispanic
```{r}
Tdap_hispanic <- Tdap_race %>%
  filter(Dimension == "Hispanic")
#plot
ggplot(Tdap_hispanic, aes(x = UninsuredRate, y = Coverage)) +
  geom_point(color = "orange", size = 2) +
  geom_smooth(method = "lm", se = TRUE, color = "darkred") +
  labs(
    title = "Tdap Coverage vs Uninsured Rate (Hispanic)",
    x = "Uninsured Rate",
    y = "Vaccination Coverage (%)"
  ) +
  theme_minimal()
#summary
summary(lm(Coverage ~ UninsuredRate, data = Tdap_hispanic))
```
Other or Multiple Races, Non-Hispanic
```{r}
Tdap_other <- Tdap_race %>%
  filter(Dimension == "Other or Multiple Races, Non-Hispanic")
#plot
ggplot(Tdap_other, aes(x = UninsuredRate, y = Coverage)) +
  geom_point(color = "purple", size = 2) +
  geom_smooth(method = "lm", se = TRUE, color = "darkred") +
  labs(title = "Tdap Coverage vs Uninsured Rate (Other or Multiple Races, Non-Hispanic)",
    x = "Uninsured Rate",
    y = "Vaccination Coverage (%)"
  ) +
  theme_minimal()
#summary
summary(lm(Coverage ~ UninsuredRate, data = Tdap_other))
```

Merged Tdap Stratified by Race
```{r}
ggplot(Tdap_race, aes(
  x = UninsuredRate,
  y = Coverage,
  color = Dimension,
  shape = Dimension
)) +
  geom_point(size = 2, alpha = 0.6) + 
  geom_smooth(method = "lm", se = TRUE, fullrange = TRUE) +
  scale_color_manual(values = my_colors) + 
  labs(
    title = "Tdap Coverage vs Uninsured Rate by Race/Ethnicity",
    x = "Uninsured Rate",
    y = "Vaccination Coverage (%)",
    color = "Race/Ethnicity",
    shape = "Race/Ethnicity"
  ) +
  theme_classic() +
  guides(color = guide_legend(override.aes = list(size = 3))) +
  theme(
    legend.text = element_text(size = 5),
    legend.title = element_text(size = 6),
    legend.key.size = unit(0.6, "lines")
  )
```


Stratified Analysis by Age Group for Influenza Vaccination
Influenza&Age
```{r}
influenza_age <- merged_df %>%
  filter(
    Vaccine == "Influenza",
    Dimension.Type == "Age",
    !is.na(Estimate....),
    !Estimate.... %in% c("NR*", "N/A", "--", "*")
  ) %>%
  mutate(
    Coverage = as.numeric(str_replace(Estimate...., "%", "")),
    Year = as.numeric(Survey.Year.Influenza.Season),
    UninsuredRate = Uninsured / (Insured + Uninsured)
  )
unique(influenza_age$Dimension)
```
>=18 Years

```{r}
influenza_18 <- influenza_age %>%
  filter(Dimension == ">=18 Years")

# Plot
ggplot(influenza_18, aes(x = UninsuredRate, y = Coverage)) +
  geom_point(color = "steelblue", size = 2) +
  geom_smooth(method = "lm", se = TRUE, color = "darkred") +
  labs(
    title = "Influenza Coverage vs Uninsured Rate (>=18 years)",
    x = "Uninsured Rate",
    y = "Vaccination Coverage (%)"
  ) +
  theme_minimal()

# Summary
summary(lm(Coverage ~ UninsuredRate, data = influenza_18))
```
18-24 Years
```{r}
influenza_1824 <- influenza_age %>%
  filter(Dimension == "18-24 Years")

# Plot
ggplot(influenza_1824, aes(x = UninsuredRate, y = Coverage)) +
  geom_point(color = "forestgreen", size = 2) +
  geom_smooth(method = "lm", se = TRUE, color = "darkred") +
  labs(
    title = "Influenza Coverage vs Uninsured Rate (18-24 Years)",
    x = "Uninsured Rate",
    y = "Vaccination Coverage (%)"
  ) +
  theme_minimal()

# Summary
summary(lm(Coverage ~ UninsuredRate, data = influenza_1824))
```
25-34 Years
```{r}
influenza_2534 <- influenza_age %>%
  filter(Dimension == "25-34 Years")

# Plot
ggplot(influenza_1824, aes(x = UninsuredRate, y = Coverage)) +
  geom_point(color = "orange", size = 2) +
  geom_smooth(method = "lm", se = TRUE, color = "darkred") +
  labs(
    title = "Influenza Coverage vs Uninsured Rate (25-34 Years)",
    x = "Uninsured Rate",
    y = "Vaccination Coverage (%)"
  ) +
  theme_minimal()

# Summary
summary(lm(Coverage ~ UninsuredRate, data = influenza_2534))
```
>=35 Years

```{r}
influenza_35 <- influenza_age %>%
  filter(Dimension == ">=35 Years")

# Plot
ggplot(influenza_1824, aes(x = UninsuredRate, y = Coverage)) +
  geom_point(color = "purple", size = 2) +
  geom_smooth(method = "lm", se = TRUE, color = "darkred") +
  labs(
    title = "Influenza Coverage vs Uninsured Rate (>=35 Years)",
    x = "Uninsured Rate",
    y = "Vaccination Coverage (%)"
  ) +
  theme_minimal()

# Summary
summary(lm(Coverage ~ UninsuredRate, data = influenza_35))
```
Merged Influenza Stratified by Age Group
```{r}
my_colors_age <- c(
  ">=18 Years" = "#44d8ee",
  "18-24 Years" = "#679436",
  "25-34 Years" = "#be0aff",   
  ">=35 Years" = "#f46197" 
)
ggplot(influenza_age, aes(
  x = UninsuredRate,
  y = Coverage,
  color = Dimension,
  shape = Dimension
)) +
  geom_point(size = 2, alpha = 0.6) + 
  geom_smooth(method = "lm", se = TRUE, fullrange = TRUE) +
  scale_color_manual(values = my_colors_age) + 
  labs(
    title = "Influenza Coverage vs Uninsured Rate by Age Group",
    x = "Uninsured Rate",
    y = "Vaccination Coverage (%)",
    color = "Age Group",
    shape = "Age Group"
  ) +
  theme_classic()
```


Stratified Analysis by Age Group for Tdap Vaccination
Tdap&Age
```{r}
Tdap_age <- merged_df %>%
  filter(
    Vaccine == "Tdap",
    Dimension.Type == "Age",
    !is.na(Estimate....),
    !Estimate.... %in% c("NR*", "N/A", "--", "*")
  ) %>%
  mutate(
    Coverage = as.numeric(str_replace(Estimate...., "%", "")),
    Year = as.numeric(Survey.Year.Influenza.Season),
    UninsuredRate = Uninsured / (Insured + Uninsured)
  )
unique(Tdap_age$Dimension)
```

>=18 Years

```{r}
Tdap_18 <- Tdap_age %>%
  filter(Dimension == ">=18 Years")

# Plot
ggplot(Tdap_18, aes(x = UninsuredRate, y = Coverage)) +
  geom_point(color = "steelblue", size = 2) +
  geom_smooth(method = "lm", se = TRUE, color = "darkred") +
  labs(
    title = "Tdap Coverage vs Uninsured Rate (>=18 years)",
    x = "Uninsured Rate",
    y = "Vaccination Coverage (%)"
  ) +
  theme_minimal()

# Summary
summary(lm(Coverage ~ UninsuredRate, data =Tdap_18))
```
18-24 Years
```{r}
Tdap_1824 <- Tdap_age %>%
  filter(Dimension == "18-24 Years")

# Plot
ggplot(Tdap_1824, aes(x = UninsuredRate, y = Coverage)) +
  geom_point(color = "darkgreen", size = 2) +
  geom_smooth(method = "lm", se = TRUE, color = "darkred") +
  labs(
    title = "Tdap Coverage vs Uninsured Rate (18-24 years)",
    x = "Uninsured Rate",
    y = "Vaccination Coverage (%)"
  ) +
  theme_minimal()

# Summary
summary(lm(Coverage ~ UninsuredRate, data =Tdap_1824))
```
25-34 Years
```{r}
Tdap_2534 <- Tdap_age %>%
  filter(Dimension == "25-34 Years")

# Plot
ggplot(Tdap_2534, aes(x = UninsuredRate, y = Coverage)) +
  geom_point(color = "orange", size = 2) +
  geom_smooth(method = "lm", se = TRUE, color = "darkred") +
  labs(
    title = "Tdap Coverage vs Uninsured Rate (25-34 years)",
    x = "Uninsured Rate",
    y = "Vaccination Coverage (%)"
  ) +
  theme_minimal()

# Summary
summary(lm(Coverage ~ UninsuredRate, data =Tdap_2534))
```
>=35 Years

```{r}
Tdap_35 <- Tdap_age %>%
  filter(Dimension == ">=35 Years")

# Plot
ggplot(Tdap_35, aes(x = UninsuredRate, y = Coverage)) +
  geom_point(color = "purple", size = 2) +
  geom_smooth(method = "lm", se = TRUE, color = "darkred") +
  labs(
    title = "Tdap Coverage vs Uninsured Rate (>=35 years)",
    x = "Uninsured Rate",
    y = "Vaccination Coverage (%)"
  ) +
  theme_minimal()

# Summary
summary(lm(Coverage ~ UninsuredRate, data =Tdap_35))
```

Merged Tdap Stratified by Age Group
```{r}
ggplot(Tdap_age, aes(
  x = UninsuredRate,
  y = Coverage,
  color = Dimension,
  shape = Dimension
)) +
  geom_point(size = 2, alpha = 0.6) + 
  geom_smooth(method = "lm", se = TRUE, fullrange = TRUE) +
  scale_color_manual(values = my_colors_age) + 
  labs(
    title = "Tdap Coverage vs Uninsured Rate by Age Group",
    x = "Uninsured Rate",
    y = "Vaccination Coverage (%)",
    color = "Age Group",
    shape = "Age Group"
  ) +
  theme_classic()
```

